---
title: "introduction"
author: "Han Xia(hanxi898), Can Wang(canwa869)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

In this vignette, we will demonstrate how to use the linreg function from the Group1Lab4 package using a well-known dataset. For illustration, we'll use the iris dataset.

The linreg function fits a linear regression model, and it comes with several methods for extracting useful information such as residuals, fitted values, coefficients, and diagnostics plots.

# Loading the package
First, we need to load the necessary packages:

{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```{r setup}
library(Group1Lab4)

# Load the package and ggplot2 for plotting
library(Group1Lab4)
library(ggplot2)
```
Next, we will fit a linear regression model using the linreg function:
```{r example}
# Fit the model using the linreg function
model <- linreg(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width, data = iris)

# Summary of the Model
# We can view a summary of the model to understand the coefficients and other statistics:

summary(model)

# Viewing Coefficients
# To see the coefficients of the fitted model:

coef(model)

# Predicted (Fitted) Values
# To obtain the predicted values from the model:

pred(model)

# Residuals
# We can also extract the residuals:

resid(model)

# Standardized Residuals
# To calculate standardized residuals, we can use the rstandard method:

rstandard(model)

# Diagnostic Plots
# Finally, we can create diagnostic plots to visualize the residuals:

plot(model)
```